### 2024-10-09 texts/paper_closing.tex
minor rephrasing/rewriting

% Created 2024-10-08 di 10:05
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than loaning or donating their collection or opening museums as a group.
This phenomenon of private collectors taking the initiative in setting up a museum of their own has become increasingly widespread, with around 80\% of currently open private museums having opened since 2000 \parencite{Velthuis_etal_2023_boom}.
To be considered as a private museum for this study, a collector needs to have amassed a substantial art collection, which he or she exhibits in a building in a way that is accessible to the public while receiving limited public and corporate funding.
The central role of the founder delimits a private museum from other organizational forms such as public museums supported by local or state governments, corporate museums run by companies or other non-profit museums operated by associations or foundations with more dispersed ownership and control.\footnote{Which is not to say that for an institution to be considered a private museum, it has to be legal personal ownership of the founder. Instead, the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms and has to be assessed on a case-by-case basis.}
\subsubsection*{Financial conditions in the cultural sector}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Oct  4 15:36:13 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & $294$ & $0.584$ & $0.604$ & $0.49$ & $0$ & $1$ \\ 
   & Gender - Female & $79$ & $0.157$ & $0.166$ & $0.37$ & $0$ & $1$ \\ 
   & Gender - Couple & $130$ & $0.258$ & $0.231$ & $0.42$ & $0$ & $1$ \\ 
   & Founder died & $NA$ & $NA$ & $0.097$ & $0.30$ & $0$ & $1$ \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & $190$ & $0.378$ & $0.408$ & $0.49$ & $0$ & $1$ \\ 
   & Self-Identification - Foundation & $104$ & $0.207$ & $0.189$ & $0.39$ & $0$ & $1$ \\ 
   & Self-Identification - Collection & $69$ & $0.137$ & $0.130$ & $0.34$ & $0$ & $1$ \\ 
   & Self-Identification - Other & $140$ & $0.278$ & $0.274$ & $0.45$ & $0$ & $1$ \\ 
   & Founder name in Museum name & $240$ & $0.477$ & $0.477$ & $0.50$ & $0$ & $1$ \\ 
   & AN Ranking - Not Included & $NA$ & $NA$ & $0.802$ & $0.40$ & $0$ & $1$ \\ 
   & AN Ranking - Included & $NA$ & $NA$ & $0.144$ & $0.35$ & $0$ & $1$ \\ 
   & AN Ranking - Dropped & $NA$ & $NA$ & $0.053$ & $0.23$ & $0$ & $1$ \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) & $NA$ & $NA$ & $0.450$ & $1.26$ & $0.00077$ & $27.26$ \\ 
   & Pop. (millions) within 10km & $NA$ & $NA$ & $1.337$ & $1.68$ & $0.000087$ & $10.81$ \\ 
   & Nbr PM within 10km & $NA$ & $NA$ & $1.778$ & $3.14$ & $0$ & $16$ \\ 
   & Great Recession (2008/09) & $NA$ & $NA$ & $0.076$ & $0.27$ & $0$ & $1$ \\ 
   & Covid Pandemic (2020/21) & $NA$ & $NA$ & $0.145$ & $0.35$ & $0$ & $1$ \\ 
   & Region - Africa & $8$ & $0.016$ & $0.012$ & $0.11$ & $0$ & $1$ \\ 
   & Region - Asia & $142$ & $0.282$ & $0.292$ & $0.45$ & $0$ & $1$ \\ 
   & Region - Europe & $248$ & $0.493$ & $0.497$ & $0.50$ & $0$ & $1$ \\ 
   & Region - Latin America & $23$ & $0.046$ & $0.042$ & $0.20$ & $0$ & $1$ \\ 
   & Region - North America & $72$ & $0.143$ & $0.138$ & $0.34$ & $0$ & $1$ \\ 
   & Region - Oceania & $10$ & $0.020$ & $0.019$ & $0.13$ & $0$ & $1$ \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

The death of the founder is not associated with a significant difference (p=0.52) in private museum closure, i.e. museums are not significantly more likely to close after their founder has died, which provides little support to H1a.\footnote{An alternative specification of founder death which partitions the time after the death into a short-term and long-term period is reported in the supplementary materials; this specification also provides little evidence for a significant effect of the death of the founder}
While the point estimate is positive (0.280, corresponding to a 32\% increase in mortality for museums whose founders have died compared to those who have not), the low risk overall means that even decade-long survival prospects do not differ substantially despite the cumulative character of risk (figure \ref{fig:p_surv_death}).

>>>>

% Created 2024-10-08 di 12:23
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{Higonnet_2003_sight,Duncan_1995_civilizing}, in recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than loaning or donating their collection or opening museums as a group.
This phenomenon of private collectors taking the initiative of setting up a museum of their own has become increasingly widespread, with around 80\% of currently open private museums having opened since 2000 \parencite{Velthuis_etal_2023_boom}.
To be considered as a private museum for this study, a collector needs to have amassed a substantial art collection, which he or she exhibits in a building in a way that is accessible to the public while receiving limited public and corporate funding.
The central role of the founder delimits a private museum from other organizational forms such as public museums supported by local or state governments, corporate museums run by companies or other non-profit museums operated by associations or foundations with more dispersed ownership and control.\footnote{Which is not to say that for an institution to be considered a private museum, it has to be legal personal ownership of the founder. Instead, the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms and has to be assessed on a case-by-case basis.}
\subsubsection*{Financial conditions in the cultural sector}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Oct  4 15:36:13 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
  \cmidrule(r){3-4}\cmidrule(r){5-8}
  \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}}                                                          \\ 
 & Gender - Male                    & $294$ & $0.584$ & $0.604$ & $0.49$ & $0$        & $1$     \\ 
 & Gender - Female                  & $79$  & $0.157$ & $0.166$ & $0.37$ & $0$        & $1$     \\ 
 & Gender - Couple                  & $130$ & $0.258$ & $0.231$ & $0.42$ & $0$        & $1$     \\ 
 & Founder died                     &       &         & $0.097$ & $0.30$ & $0$        & $1$     \\ 
   \multicolumn{8}{l}{\textbf{Museum}}                                                          \\ 
 & Self-Identification - Museum     & $190$ & $0.378$ & $0.408$ & $0.49$ & $0$        & $1$     \\ 
 & Self-Identification - Foundation & $104$ & $0.207$ & $0.189$ & $0.39$ & $0$        & $1$     \\ 
 & Self-Identification - Collection & $69$  & $0.137$ & $0.130$ & $0.34$ & $0$        & $1$     \\ 
 & Self-Identification - Other      & $140$ & $0.278$ & $0.274$ & $0.45$ & $0$        & $1$     \\ 
 & Founder name in Museum name      & $240$ & $0.477$ & $0.477$ & $0.50$ & $0$        & $1$     \\ 
 & AN Ranking - Not Included        &       &         & $0.802$ & $0.40$ & $0$        & $1$     \\ 
 & AN Ranking - Included            &       &         & $0.144$ & $0.35$ & $0$        & $1$     \\ 
 & AN Ranking - Dropped             &       &         & $0.053$ & $0.23$ & $0$        & $1$     \\ 
   \multicolumn{8}{l}{\textbf{Environment}}                                                     \\ 
 & PM density (country)             &       &         & $0.450$ & $1.26$ & $0.00077$  & $27.26$ \\ 
 & Pop. (millions) within 10km      &       &         & $1.337$ & $1.68$ & $0.000087$ & $10.81$ \\ 
 & Nbr PM within 10km               &       &         & $1.778$ & $3.14$ & $0$        & $16$    \\ 
 & Great Recession (2008/09)        &       &         & $0.076$ & $0.27$ & $0$        & $1$     \\ 
 & Covid Pandemic (2020/21)         &       &         & $0.145$ & $0.35$ & $0$        & $1$     \\ 
 & Region - Africa                  & $8$   & $0.016$ & $0.012$ & $0.11$ & $0$        & $1$     \\ 
 & Region - Asia                    & $142$ & $0.282$ & $0.292$ & $0.45$ & $0$        & $1$     \\ 
 & Region - Europe                  & $248$ & $0.493$ & $0.497$ & $0.50$ & $0$        & $1$     \\ 
 & Region - Latin America           & $23$  & $0.046$ & $0.042$ & $0.20$ & $0$        & $1$     \\ 
 & Region - North America           & $72$  & $0.143$ & $0.138$ & $0.34$ & $0$        & $1$     \\ 
 & Region - Oceania                 & $10$  & $0.020$ & $0.019$ & $0.13$ & $0$        & $1$     \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

The death of the founder is not associated with a significant difference (p=0.52) in private museum closure, i.e. museums are not significantly more likely to close after their founder has died, which provides little support to H1a.\footnote{An alternative specification of founder death which partitions the time after the death into a short-term and long-term period is reported in the supplementary materials; this specification also provides little evidence for a significant effect of the death of the founder.}
While the point estimate is positive (0.280, corresponding to a 32\% increase in mortality for museums whose founders have died compared to those who have not), the low risk overall means that even decade-long survival prospects do not differ substantially despite the cumulative character of risk (figure \ref{fig:p_surv_death}).
